Designing for Complex Gig Work and Careers

### 2017-03-07 proposals/SIGFproposal_2017/ali_alkhatib_sigf.tex
abstract revision --- 98 words!

\begin{document}
  % \maketitle
  \begin{abstract}
On--demand labor has become a new instantiation of piecework.
Without shared factories and water coolers,
how do these workers coordinate,
build solidarity,
and take collective action?
We will engage in fieldwork with pieceworkers in data entry,
domestic services,
and on--demand driving to understand how they counter algorithmic systems and engage in collective action.
Our goal is to both understand the factors that drive collective behavior in supposedly distributed labor platforms,
and to build infrastructures that enable the growth of worker collective action in digitally mediated on--demand labor.
Our results shed light on the potential for digital piecework cooperativism,
as well as the policies necessary for it to succeed. % ~108 words
  \end{abstract}

>>>>

\begin{document}
  % \maketitle
  \begin{abstract}
Gig work has become a new instantiation of piecework.
Further, gig work platforms allow employers to geographically disperse workers and silo workers' information,
making organization and coordination all but impossible,
and stymieing work specialization and expertise.
Our research will draw on our past work, using historical analysis of piecework to inform this contemporary phenomenon,
to design and develop a ``digital hiring hall''.
Our research will
shed light on the potential complexity limits of gig work,
point to possible futures of labor advocacy for gig workers,
and offer some insights into the best practices of principally online collective governance.

% The results of this research will make it easier for gig workers to identify and focus on specializations,
% fostering rewarding careers in gig work and giving workers spaces to organize and coordinate.

% Our goal is to both understand the factors that drive collective behavior in supposedly distributed labor platforms,
% and to build infrastructures that enable the growth of worker collective action in digitally mediated on--demand labor.
% Our results shed light on the potential for digital piecework cooperativism,
% as well as the policies necessary for it to succeed. % ~108 words
  \end{abstract}
